---
title: Supplement for Social overtures in Corydoradinae catfish mitigate the effects of acute stress
execute:
  warning: false
  error: false
  message: false
format:
  html:
    code-fold: true
    code-summary: "Show code"
    toc: true
    toc-depth: 2
self-contained: true
---

```{r packages, include = FALSE}

# Load required packages
packages <- c(
  'broom.mixed',
  'cAIC4',
  'emmeans',        # Post-hoc test for respiration rate change by period
  'ggeffects',      # For Partial Effects Plots
  'glmmTMB',        # For negative binomial models
  'gt',             # For generating readable summaries 
  'influence.ME',   # Check for influential observations
  'kableExtra',     # For table generation and formatting
  'lme4',           # For running mixed effect models
  'lmerTest',       # For p-values with mixed effects models
  'MASS',           # For dropterm function
  'mice',           # For multiple imputation
  'MuMIn',          # For easier model selection
  'patchwork',      # For arranging multiple plots
  'performance',    # For diagnostic checks
  'psych',          # For factor analysis
  'tidyverse'       # Multiple essential packages
  )

for (pkg in packages) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg, dependencies = TRUE)
    library(pkg, character.only = TRUE)
  }
}
```

# Data Import and Cleaning
```{r import}

# Import CSV file
df <- read.csv("corrected_data.csv")|>
  filter(Group.ID != 5151) |>  # Remove group 
  select(
    -date, -date.formate, -test.tank, -time.to.first.nudge, -scorer, 
    -back.nudges.first, -mutuals.first, -back.nudges.second, -mutuals.second, 
    -nudge.period.same.as.first.five.minutes., 
    -nudge.period.same.as.second.five.minutes., -second.period.activity.check
  )


# Rename variables
names(df) <- c(
  "sex", "group_id", "fish_number", "fish_id", 
  "nudges_first", "nudges_second", "surfing_first", "surfing_second", 
  "activity_first", "activity_second", "feed_time", "freeze_time", 
  "resp_first", "resp_2", "resp_3", "resp_second", "length"
  )

# Reorder variables
df <- df |> 
  select(
    group_id, fish_number, fish_id, sex, length, activity_first, 
    resp_first, nudges_first, surfing_first, resp_2, resp_3, activity_second, 
    resp_second, nudges_second, surfing_second, feed_time, freeze_time
    )
```

```{r clean}
df$resp_3[df$resp_3 == "na"] <- NA # Fix some errant NA encodings

df <- df |> 
  mutate(
    group_id = as.factor(group_id),
    fish_number = as.factor(fish_number),
    fish_id = as.factor(fish_id),
    sex = as.factor(sex),
    resp_3 = as.numeric(resp_3)
  )
```

```{r}
# Create nudges per activity metric
df <- df |> 
  mutate(
    ann_first = round(ifelse(activity_first != 0, (nudges_first / activity_first) * 60, 0), 2),
    ann_second = round(ifelse(activity_second != 0, (nudges_second / activity_second) * 60, 0), 2)
  )

# Create foraging time metric
df <- df |> 
  mutate(
    forage_time = feed_time - freeze_time
  )
```

## Respiration Rate Data (Multiple Imputation)
```{r}
# Assemble long data and flag missing rows
df_resp <- bind_rows(
  df |> transmute(group_id, fish_id, sex, period = "Interval 1", resp = resp_first),
  df |> transmute(group_id, fish_id, sex, period = "Interval 2", resp = resp_2),
  df |> transmute(group_id, fish_id, sex, period = "Interval 3", resp = resp_3),
  df |> transmute(group_id, fish_id, sex, period = "Interval 4", resp = resp_second)
) |> 
  mutate(period = factor(period, levels = paste("Interval", 1:4)),
         missing_orig = is.na(resp))

# Multiple imputation (20 draws)
set.seed(2679)
imp <- mice(df_resp, m = 20, method = "rf", printFlag = FALSE)

# Build plot data from imputed values
long_imp <- map_dfr(seq_len(imp$m), ~ complete(imp, .x) |>
                      mutate(draw = .x))

plotdat <- long_imp |> 
  select(-missing_orig) |>
  left_join(df_resp |> 
              select(group_id, fish_id, period, missing_orig),
            by = c("group_id", "fish_id", "period")) |> 
  group_by(group_id, fish_id, period, missing_orig) |> 
  summarise(resp = mean(resp), .groups = "drop") |> 
  mutate(point_type = if_else(missing_orig, "Imputed", "Observed"))
```




## Dataset Construction
```{r long}
df_np1 <- df |> 
  transmute(
    group_id,
    fish_id,
    sex,
    length,
    activity = activity_first,
    resp = resp_first,
    nudges = nudges_first,
    ann = ann_first,
    surfing = surfing_first,
    period = factor("Period 1", levels = c("Period 1", "Period 2"))
  )

df_np2 <- df |> 
  transmute(
    group_id,
    fish_id,
    sex,
    length,
    activity = activity_second,
    resp = resp_second,
    nudges = nudges_second,
    ann = ann_second,
    surfing = surfing_second,
    period = factor("Period 2", levels = c("Period 1", "Period 2"))
  ) |> 
  filter(!is.na(resp))

df_long <- bind_rows(df_np1, df_np2)
```

```{r}
# Select only cases with complete data for second respiration period
df_complete_resp <- df[!is.na(df$resp_second), ]
```

 

# Model Specification and Selection

Before fitting any models, we examined the distribution of each response variable to choose an appropriate statistical family. Histograms of all variables are shown below, followed by formal overdispersion checks for count variables.
```{r}

# Set layout
par(mfrow = c(6, 3), mar = c(3, 3, 2, 1))

# Activity: integer values >= 0
hist(df$activity_first, main = "Activity (Period 1)", xlab = "")
hist(df$activity_second, main = "Activity (Period 2)", xlab = "")
hist(df_long$activity, main = "Activity (Pooled)", xlab = "")

# ANN: real values >= 0
hist(df$ann_first, main = "ANN (Period 1)", xlab = "")
hist(df$ann_second, main = "ANN (Period 2)", xlab = "")
hist(df_long$ann, main = "ANN (Pooled)", xlab = "")

# Nudges: integer values >= 0
hist(df$nudges_first, main = "Nudges (Period 1)", xlab = "")
hist(df$nudges_second, main = "Nudges (Period 2)", xlab = "")
hist(df_long$nudges, main = "Nudges (Pooled)", xlab = "")

# Respiratory Rate: continuous values > 0
hist(df$resp_first, main = "Resp (Period 1)", xlab = "")
hist(df_complete_resp$resp_second, main = "Resp (Period 2)", xlab = "")
hist(df_long$resp, main = "Resp (Pooled)", xlab = "")

# Wall Surfing: integer values >= 0
hist(df$surfing_first, main = "Surfing (Period 1)", xlab = "")
hist(df$surfing_second, main = "Surfing (Period 2)", xlab = "")
hist(df_long$surfing, main = "Surfing (Pooled)", xlab = "")

# Foraging outcomes: Integer values >= 0
hist(df$feed_time, main = "Feed Time", xlab = "")
hist(df$freeze_time, main = "Freeze Time", xlab = "")
hist(df$forage_time, main = "Forage Time", xlab = "")

par(mfrow = c(1, 1), mar = c(5, 4, 4, 2))  # reset
```

```{r}
base_summ <- df |> 
  summarize(across(c(activity_first, activity_second,
                     nudges_first, nudges_second,
                     surfing_first, surfing_second,
                     feed_time, freeze_time, forage_time),
                   list(mean = ~mean(., na.rm = TRUE),
                        variance = ~var(., na.rm = TRUE)),
                   .names = "{.col}_{.fn}")) |> 
  pivot_longer(everything()) |> 
  separate(name, into = c("variable", "stat"), sep = "_(?=[^_]+$)") |> 
  pivot_wider(names_from = stat, values_from = value) |> 
  mutate(ratio = variance / mean, dataset = "df (wide)")


long_summ <- df_long |> 
  summarize(across(c(activity, nudges, surfing),
                   list(mean = ~mean(., na.rm = TRUE),
                        variance = ~var(., na.rm = TRUE)),
                   .names = "{.col}_{.fn}")) |>
  pivot_longer(everything()) |>
  separate(name, into = c("variable", "stat"), sep = "_(?=[^_]+$)") |>
  pivot_wider(names_from = stat, values_from = value) |>
  mutate(ratio = variance / mean,
         dataset = "df_long (pooled)")

bind_rows(base_summ, long_summ) |>
  select(dataset, variable, mean, variance, ratio) |>
  arrange(dataset, variable) |>
  kable(digits = 2,
        col.names = c("Dataset", "Variable", "Mean", "Variance", "Variance/Mean"),
        caption = "Overdispersion assessment for count variables") |>
  kableExtra::kable_styling() |>
  kableExtra::collapse_rows(columns = 1, valign = "top")
```
All count and duration variables (activity, nudges, wall surfing, feed time, freeze time, and active foraging time) showed substantial overdispersion, which rules out a Poisson distribution and justifies using a negative binomial distribution instead.

Nudging rate while active (ANN) is a continuous rate rather than a count, but has a natural point mass at zero for fish that were completely inactive. Rather than fitting a more complex hurdle model, we used a Tweedie distribution with a log link, which handles this mixture of zeros and positive continuous values in a single model. Posterior predictive checks confirmed adequate fit, with one exception noted below.
```{r}
ann_1_model <- glmmTMB(ann_first ~ 1, family = tweedie(link = "log"), data = df)
ann_2_model <- glmmTMB(ann_second ~ 1, family = tweedie(link = "log"), data = df)
ann_model <- glmmTMB(ann ~ 1, family = tweedie(link = "log"), data = df_long)

check_overdispersion(ann_1_model)
check_overdispersion(ann_2_model)
check_overdispersion(ann_model)

check_predictions(ann_1_model)
check_predictions(ann_2_model)
check_predictions(ann_model)
```
One fish with very low, but non-zero, activity produced an extreme ANN value in the first nudging period that was not captured in the replicated data.



Respiration rate was modeled with a Gaussian (normal) distribution, as it is a continuous physiological measurement with no natural floor or ceiling. Diagnostic checks on intercept-only models confirmed this was appropriate.
```{r}
resp_1_null <- lmer(resp_first ~ 1 + (1 | group_id), data = df, na.action = na.omit)
resp_2_null <- lmer(resp_second ~ 1 + (1 | group_id), data = df_complete_resp, na.action = na.omit)
resp_null <- lmer(resp ~ 1 + (1 | fish_id) + (1 | group_id), data = df_long, na.action = na.omit)
check_model(resp_1_null)
check_model(resp_2_null)
check_model(resp_null)
```
Reasonably good fits with irregularities in influential observations reflecting the small sample size and large variance.

## Zero-inflation Diagnostics

Zero-inflation for candidate outcome variables was assessed by fitting intercept-only negative binomial models and comparing observed versus predicted zero counts. Feed time, freeze time, and active foraging time were excluded as no zero values were observed for these variables.
```{r}
# Function to format p-values
fmt_p <- function(p) {
  if_else(is.na(p), NA_character_,
    if_else(p < 0.001, "< 0.001",
      as.character(round(p, 3))
    )
  )
}

zi_models <- list(
  act_2  = glmmTMB(activity_second ~ 1, family = nbinom2(), data = df),
  act    = glmmTMB(activity        ~ 1, family = nbinom2(), data = df_long),
  ann_2  = glmmTMB(ann_second   ~ 1, family = nbinom2(), data = df),
  ann    = glmmTMB(ann          ~ 1, family = nbinom2(), data = df_long),
  surf_2 = glmmTMB(surfing_second  ~ 1, family = nbinom2(), data = df),
  surf   = glmmTMB(surfing         ~ 1, family = nbinom2(), data = df_long)
)

zi_results <- map_dfr(zi_models, function(m) {
  r <- check_zeroinflation(m)
  data.frame(
    observed    = r$observed.zeros,
    predicted   = round(r$predicted.zeros, 1),
    ratio       = round(r$ratio, 2),
    p_numeric   = r$p.value
  )
}, .id = "model") |>
  mutate(
    variable    = case_match(model,
      "act_2"  ~ "Activity",    "act"  ~ "Activity",
      "ann_2"  ~ "ANN",      "ann"  ~ "ANN",
      "surf_2" ~ "Wall Surfing","surf" ~ "Wall Surfing"
    ),
    dataset     = case_match(model,
      "act_2"  ~ "Individual: Period 2", "ann_2" ~ "Individual: Period 2", "surf_2" ~ "Individual: Period 2",
      "act"    ~ "Pooled",   "ann"   ~ "Pooled",   "surf"   ~ "Pooled"
    ),
    significant = if_else(p_numeric < 0.05, "Yes", "No"),
    p           = fmt_p(p_numeric)  # format after comparison
  ) |>
  select(variable, dataset, observed, predicted, ratio, p, significant)

zi_results |>
  gt() |>
  cols_label(
    variable    = "Variable",
    dataset     = "Dataset",
    observed    = "Observed Zeros",
    predicted   = "Predicted Zeros",
    ratio       = "Ratio",
    p           = "p-value",
    significant = "Zero-inflated?"
  ) |>
  tab_header(title = "Zero-inflation diagnostics for count variables") |>
  tab_source_note("Ratio = observed/predicted zeros. Significant p-value (< 0.05) indicates zero-inflation.") |>
  tab_options(table.width = pct(100))
```
Activity showed significant zero-inflation in Period 2 and pooled datasets (p = 0.008 and p < 0.001); Period 1 was borderline (p = 0.064). Wall surfing showed significant zero-inflation in Period 2 only. Nudges showed no zero-inflation. Models were specified accordingly, with `ziformula = ~1` included where significant zero-inflation was detected.


## Random Effect Structure Selection
Random effect structure for all pooled dataset models was evaluated by comparing models of the form `outcome ~ period + (1 | fish_id)` vs. `outcome ~ period + (1 | fish_id) + (1 | group_id)` using AICc. Fish ID was included as a baseline random intercept in all pooled models to account for the repeated measures structure. For individual-level dataset models, each fish appears only once, making fish ID a saturated random effect that cannot estimate variance, and Group ID is the only appropriate random effect for these models, so no selection was necessary.
```{r}
activity_nb_fish  <- glmmTMB(activity ~ period + (1 | fish_id), family = nbinom2, ziformula = ~1, data = df_long)
activity_nb_multi <- glmmTMB(activity ~ period + (1 | fish_id) + (1 | group_id), family = nbinom2, ziformula = ~1, data = df_long)
ann_tw_fish       <- glmmTMB(ann ~ period + (1 | fish_id), family = tweedie(link = "log"), data = df_long)
ann_tw_multi      <- glmmTMB(ann ~ period + (1 | fish_id) + (1 | group_id), family = tweedie(link = "log"), data = df_long)
nudges_nb_fish    <- glmmTMB(nudges ~ period + (1 | fish_id), family = nbinom2, data = df_long)
nudges_nb_multi   <- glmmTMB(nudges ~ period + (1 | fish_id) + (1 | group_id), family = nbinom2, data = df_long)
resp_g_fish       <- lmer(resp ~ period + (1 | fish_id), data = df_long)
resp_g_multi      <- lmer(resp ~ period + (1 | fish_id) + (1 | group_id), data = df_long)
surfing_nb_fish   <- glmmTMB(surfing ~ period + (1 | fish_id), family = nbinom2, ziformula = ~1, data = df_long)
surfing_nb_multi  <- glmmTMB(surfing ~ period + (1 | fish_id) + (1 | group_id), family = nbinom2, ziformula = ~1, data = df_long)

# Check for singular fits in multilevel candidates
is_singular_glmmtmb <- function(model) {
  re_var <- as.data.frame(VarCorr(model)$cond)
  any(re_var$vcov < 1e-6)
}

singular_checks <- data.frame(
  Model    = c("Activity", "ANN", "Nudges", "Resp Rate", "Wall Surfing"),
  Singular = c(
    is_singular_glmmtmb(activity_nb_multi),
    is_singular_glmmtmb(ann_tw_multi),
    is_singular_glmmtmb(nudges_nb_fish),
    isSingular(resp_g_multi),          # lmer - isSingular works fine
    is_singular_glmmtmb(surfing_nb_multi)
  )
)

aicc_tbl <- data.frame(
  Behaviour = c("Activity", "ANN", "Nudges", "Resp Rate", "Wall Surfing"),
  aicc_fish  = c(AICc(activity_nb_fish), AICc(ann_tw_fish), AICc(nudges_nb_fish),
                 AICc(resp_g_fish),      AICc(surfing_nb_fish)),
  aicc_multi = c(AICc(activity_nb_multi), AICc(ann_tw_multi), AICc(nudges_nb_multi),
                 AICc(resp_g_multi),       AICc(surfing_nb_multi))
) |>
  mutate(
    delta    = round(aicc_fish - aicc_multi, 2),
    selected = case_when(
      delta >  2 ~ "fish_id + group_id",
      delta < -2 ~ "fish_id only",
      TRUE       ~ "fish_id + group_id"
    ),
    aicc_fish  = round(aicc_fish, 2),
    aicc_multi = round(aicc_multi, 2),
    singular   = singular_checks$Singular
  )

aicc_tbl |>
  gt() |>
  cols_label(
    Behaviour  = "Behaviour",
    aicc_fish  = "AICc (fish only)",
    aicc_multi = "AICc (fish + group)",
    delta      = "Δ AICc",
    selected   = "Selected Structure",
    singular   = "Singular Fit?"
  ) |>
  tab_header(title = "Random effect structure selection via AICc (pooled dataset models)") |>
  tab_source_note("Δ AICc = AICc(fish only) − AICc(fish + group). Positive values favour the multilevel model. Models within 2 AICc units are considered equivalent; the multilevel model was retained in ties. Singular fit indicates fish-level variance was estimated at zero.") |>
  tab_options(table.width = pct(100))
```

Activity, respiratory rate, and wall surfing favored the multilevel structure (ΔAICc > 2), while ANN and nudges favored the fish-only model (ΔAICc < -2), suggesting these behaviors do not show meaningful within-pair similarity beyond individual variation. The respiratory rate multilevel model produced a singular fit, with fish-level variance estimated at zero, indicating that pair-level clustering alone accounted for the random variation in respiratory rate. The multilevel structure was nonetheless retained for consistency with the other behavioral variables where it was selected.

# Descriptive Statistics

```{r}
make_desc <- function(data, vars, var_labels, period_label) {
  data |>
    group_by(sex) |>
    summarise(
      across(all_of(vars), 
             ~paste0(round(mean(., na.rm = TRUE), 2), 
                    " (", round(sd(., na.rm = TRUE), 2), ")",
                    " [", round(min(., na.rm = TRUE), 2),
                    "–", round(max(., na.rm = TRUE), 2), "]")),
      .groups = "drop"
    ) |>
    pivot_longer(-sex, names_to = "variable", values_to = "summary") |>
    mutate(
      variable = var_labels[variable],
      period   = period_label
    )
}

make_desc_overall <- function(data, vars, var_labels, period_label) {
  data |>
    summarise(
      across(all_of(vars), 
             ~paste0(round(mean(., na.rm = TRUE), 2), 
                    " (", round(sd(., na.rm = TRUE), 2), ")",
                    " [", round(min(., na.rm = TRUE), 2),
                    "–", round(max(., na.rm = TRUE), 2), "]")),
      .groups = "drop"
    ) |>
    pivot_longer(everything(), names_to = "variable", values_to = "summary") |>
    mutate(
      variable = var_labels[variable],
      period   = period_label,
      sex      = "Overall"
    )
}

p1_stats <- bind_rows(
  make_desc(df, c("activity_first", "ann_first", "nudges_first", "resp_first", "surfing_first"),
            c(activity_first = "Activity (s)", ann_first = "ANN", nudges_first = "Nudges",
              resp_first = "Resp Rate", surfing_first = "Wall Surfing (s)"), "Period 1"),
  make_desc_overall(df, c("activity_first", "ann_first", "nudges_first", "resp_first", "surfing_first"),
            c(activity_first = "Activity (s)", ann_first = "ANN", nudges_first = "Nudges",
              resp_first = "Resp Rate", surfing_first = "Wall Surfing (s)"), "Period 1")
)

p2_stats <- bind_rows(
  make_desc(df, c("activity_second", "ann_second", "nudges_second", "resp_second", "surfing_second"),
            c(activity_second = "Activity (s)", ann_second = "ANN", nudges_second = "Nudges",
              resp_second = "Resp Rate", surfing_second = "Wall Surfing (s)"), "Period 2"),
  make_desc_overall(df, c("activity_second", "ann_second", "nudges_second", "resp_second", "surfing_second"),
            c(activity_second = "Activity (s)", ann_second = "ANN", nudges_second = "Nudges",
              resp_second = "Resp Rate", surfing_second = "Wall Surfing (s)"), "Period 2")
)

length_stats <- bind_rows(
  make_desc(df, c("length"), c(length = "Length (cm)"), "—"),
  make_desc_overall(df, c("length"), c(length = "Length (cm)"), "—")
)

foraging_stats <- bind_rows(
  make_desc(df, c("feed_time", "freeze_time"),
            c(feed_time = "Feed Time (s)", freeze_time = "Freeze Time (s)"), "Foraging"),
  make_desc_overall(df, c("feed_time", "freeze_time"),
            c(feed_time = "Feed Time (s)", freeze_time = "Freeze Time (s)"), "Foraging")
)

bind_rows(p1_stats, p2_stats, foraging_stats, length_stats) |>
  pivot_wider(names_from = sex, values_from = summary) |>
  select(variable, period, Overall, Female, Male) |>
  arrange(variable, period) |>
  gt() |>
  cols_label(
    variable = "Variable",
    period   = "Period",
    Overall  = "Overall",
    Female   = "Female",
    Male     = "Male"
  ) |>
  tab_header(title = "Descriptive statistics by sex and monitoring period") |>
  tab_source_note("Values shown as mean (SD) [min–max].") |>
  tab_row_group(label = "Freeze Time (s)",   rows = variable == "Freeze Time (s)") |>
  tab_row_group(label = "Feed Time (s)",     rows = variable == "Feed Time (s)") |>
  tab_row_group(label = "Wall Surfing (s)",  rows = variable == "Wall Surfing (s)") |>
  tab_row_group(label = "Resp Rate",         rows = variable == "Resp Rate") |>
  tab_row_group(label = "Nudges",            rows = variable == "Nudges") |>
  tab_row_group(label = "ANN",               rows = variable == "ANN") |>
  tab_row_group(label = "Activity (s)",      rows = variable == "Activity (s)") |>
  tab_row_group(label = "Length (cm)",       rows = variable == "Length (cm)") |>
  cols_hide(variable) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()
  ) |>
  tab_options(table.width = pct(100))
```


## Between Period Differences
To assess whether behavioral variables differed between nudging periods, we fit mixed-effects regression models with period as the sole fixed effect, using the random effect structures selected in Step 2. We additionally examined whether period effects differed between sexes using pairwise Wilcoxon rank-sum tests (count and rate variables) and t-tests (respiratory rate), applied both within and between periods.
```{r}
period_models <- list(
  Activity = activity_nb_multi,
  ANN = ann_tw_fish,
  Nudges = nudges_nb_multi,
  `Resp Rate` = resp_g_multi,
  `Wall Surfing` = surfing_nb_multi
)

period_tbl <- map_dfr(period_models,
  ~tidy(.x, effects = "fixed") |>
    filter(term == "periodPeriod 2") |>
    select(estimate, std.error, statistic, p.value),
  .id = "Behaviour"
) |>
  mutate(
    display_estimate = if_else(Behaviour == "Resp Rate", estimate, exp(estimate)),
    log_estimate = if_else(Behaviour == "Resp Rate", NA_real_, estimate)
  )

# Count and Tweedie models
period_tbl |>
  filter(Behaviour != "Resp Rate") |>
  mutate(
    IRR     = round(exp(estimate), 3),
    log_est = round(log_estimate, 3),
    se      = round(std.error, 3),
    stat    = round(statistic, 3),
    p       = fmt_p(p.value)
  ) |>
  select(Behaviour, log_est, IRR, se, stat, p) |>
  gt() |>
  cols_label(
    Behaviour = "Behaviour",
    log_est   = "Log Estimate",
    IRR       = "IRR",
    se        = "SE",
    stat      = "z",
    p         = "p-value"
  ) |>
  tab_header(title = "Period effects: count and Tweedie models (Period 2 vs Period 1)") |>
  tab_source_note("IRR = incidence rate ratio; values > 1 indicate higher rates in Period 2.") |>
  tab_options(table.width = pct(100))

# Gaussian model
period_tbl |>
  filter(Behaviour == "Resp Rate") |>
  mutate(
    est  = round(estimate, 3),
    se   = round(std.error, 3),
    stat = round(statistic, 3),
    p    = fmt_p(p.value)
  ) |>
  select(Behaviour, est, se, stat, p) |>
  gt() |>
  cols_label(
    Behaviour = "Behaviour",
    est       = "Estimate (breaths/min)",
    se        = "SE",
    stat      = "t",
    p         = "p-value"
  ) |>
  tab_header(title = "Period effect: respiratory rate (Period 2 vs Period 1)") |>
  tab_source_note("Estimate represents mean difference in breaths per minute.") |>
  tab_options(table.width = pct(100))
```

Mixed-effects regression models confirmed significant period effects for all behavioral variables, with activity, ANN, nudges, and wall surfing all substantially higher in Period 2 (all IRR > 2, all p < 0.001). Respiratory rate declined significantly between periods by approximately 19.5 breaths per minute (p < 0.001).


```{r}
# Helper functions
wx_p <- function(x, y, paired = FALSE) suppressWarnings(wilcox.test(x, y, paired = paired)$p.value)
tt_p <- function(x, y, paired = FALSE) t.test(x, y, paired = paired)$p.value

f <- df$sex == "Female"
m <- df$sex == "Male"

# Get overall period p-values from regression models
overall_p <- map_dfr(period_models,
  ~tidy(.x, effects = "fixed") |>
    filter(term == "periodPeriod 2") |>
    select(p.value),
  .id = "Behaviour"
)

# Build wide table
comparison_tbl <- tribble(
  ~Comparison,
  "Overall (regression)",
  "P1: Female vs Male",
  "P2: Female vs Male",
  "Female: P1 vs P2",
  "Male: P1 vs P2"
) |>
  mutate(
    Activity = c(
      fmt_p(overall_p$p.value[overall_p$Behaviour == "Activity"]),
      fmt_p(wx_p(df$activity_first[f],  df$activity_first[m])),
      fmt_p(wx_p(df$activity_second[f], df$activity_second[m])),
      fmt_p(wx_p(df$activity_first[f],  df$activity_second[f], paired = TRUE)),
      fmt_p(wx_p(df$activity_first[m],  df$activity_second[m], paired = TRUE))
    ),
    ANN = c(
      fmt_p(overall_p$p.value[overall_p$Behaviour == "ANN"]),
      fmt_p(wx_p(df$ann_first[f],  df$ann_first[m])),
      fmt_p(wx_p(df$ann_second[f], df$ann_second[m])),
      fmt_p(wx_p(df$ann_first[f],  df$ann_second[f], paired = TRUE)),
      fmt_p(wx_p(df$ann_first[m],  df$ann_second[m], paired = TRUE))
    ),
    Nudges = c(
      fmt_p(overall_p$p.value[overall_p$Behaviour == "Nudges"]),
      fmt_p(wx_p(df$nudges_first[f],  df$nudges_first[m])),
      fmt_p(wx_p(df$nudges_second[f], df$nudges_second[m])),
      fmt_p(wx_p(df$nudges_first[f],  df$nudges_second[f], paired = TRUE)),
      fmt_p(wx_p(df$nudges_first[m],  df$nudges_second[m], paired = TRUE))
    ),
    `Resp Rate` = c(
      fmt_p(overall_p$p.value[overall_p$Behaviour == "Resp Rate"]),
      fmt_p(tt_p(df$resp_first[f],  df$resp_first[m])),
      fmt_p(tt_p(df$resp_second[f], df$resp_second[m])),
      fmt_p(tt_p(df$resp_first[f],  df$resp_second[f], paired = TRUE)),
      fmt_p(tt_p(df$resp_first[m],  df$resp_second[m], paired = TRUE))
    ),
    `Wall Surfing` = c(
      fmt_p(overall_p$p.value[overall_p$Behaviour == "Wall Surfing"]),
      fmt_p(wx_p(df$surfing_first[f],  df$surfing_first[m])),
      fmt_p(wx_p(df$surfing_second[f], df$surfing_second[m])),
      fmt_p(wx_p(df$surfing_first[f],  df$surfing_second[f], paired = TRUE)),
      fmt_p(wx_p(df$surfing_first[m],  df$surfing_second[m], paired = TRUE))
    )
  )

comparison_tbl |>
  gt() |>
  cols_label(
    Comparison    = "Comparison",
    Activity      = "Activity",
    ANN           = "ANN",
    Nudges        = "Nudges",
    `Resp Rate`   = "Resp Rate",
    `Wall Surfing` = "Wall Surfing"
  ) |>
  tab_header(title = "Period and sex comparisons across behavioral variables") |>
  tab_source_note("Overall period effect p-values are from mixed-effects regression models. Between-sex comparisons use Wilcoxon rank-sum tests (activity, ANN, nudges, wall surfing) or independent t-tests (respiratory rate). Within-sex between-period comparisons use paired versions of the same tests.") |>
  tab_options(table.width = pct(100))
```

Sex-specific comparisons revealed that both females and males showed significant increases in activity, nudges, and wall surfing between periods, while males showed no significant change in ANN (p = 0.508), consistent with the sex × period interaction observed in the intrinsic models. No significant between-sex differences were detected in Period 1 for any variable. In Period 2, ANN and nudges differed significantly between sexes (p = 0.007 and p = 0.013 respectively), driven by the divergent ANN trajectories across periods.

## Body Length by Sex

Body length was compared between sexes using a Welch two-sample t-test, as females and males were independent groups. Length was included as a covariate in intrinsic models given its potential influence on behavioral measures.

```{r}
length_tbl <- t.test(length ~ sex, data = df)

data.frame(
  Female_mean = round(length_tbl$estimate[1], 3),
  Male_mean   = round(length_tbl$estimate[2], 3),
  Difference  = round(diff(rev(length_tbl$estimate)), 3),
  t           = round(length_tbl$statistic, 3),
  df          = round(length_tbl$parameter, 2),
  p.value     = fmt_p(length_tbl$p.value),
  CI          = paste0("(", round(length_tbl$conf.int[1], 3),
                       ", ", round(length_tbl$conf.int[2], 3), ")")
) |>
  gt() |>
  cols_label(
    Female_mean = "Female Mean (cm)",
    Male_mean   = "Male Mean (cm)",
    Difference  = "Difference (cm)",
    t           = "t",
    df          = "df",
    p.value     = "p-value",
    CI          = "95% CI"
  ) |>
  tab_header(title = "Body length comparison between sexes") |>
  tab_source_note("Welch two-sample t-test. Difference = Female mean − Male mean.") |>
  tab_options(table.width = pct(100))
```

# Statistical Models
For all of the following, p-values for interaction terms and covariates are from likelihood ratio tests; p-values for main effects retained due to model hierarchy are from z-tests (glmmTMB models) or t-tests (lmer models). Adjusted p-values computed using the Benjamini-Hochberg method.

```{r}
# Create functions to generate tables of model summaries

get_lrt <- function(model) {
  tryCatch({
    d <- dropterm(model, test = "Chisq")
    lrt_df <- data.frame(
      term_short = rownames(d),
      LRT        = round(d[, "LRT"], 3),
      p_lrt      = d[, "Pr(Chi)"],
      row.names  = NULL
    ) |>
      filter(term_short != "<none>", !is.na(LRT))
    
    tidy_terms <- tidy(model, effects = "fixed") |>
      select(term) |>
      mutate(term_short = term)
    
    lrt_df$term <- sapply(lrt_df$term_short, function(short) {
      parts <- strsplit(short, ":")[[1]]
      matches <- tidy_terms$term[sapply(tidy_terms$term, function(t) {
        all(sapply(parts, function(p) grepl(p, t, fixed = TRUE)))
      })]
      if (length(matches) == 1) matches else NA_character_
    })
    
    lrt_df |>
      select(term, LRT, p_lrt) |>
      filter(!is.na(term))
  }, error = function(e) data.frame(term = character(0), LRT = numeric(0), p_lrt = numeric(0)))
}

fmt_p_lrt <- function(p, lrt) {
  lrt_fmt <- if_else(is.na(lrt), NA_character_, as.character(round(lrt, 3)))
  case_when(
    is.na(p) ~ "—",
    !is.na(lrt_fmt) ~ paste0(p, " (", lrt_fmt, ")"),
    TRUE ~ p
  )
}

format_glmmtmb <- function(model, title = "", formula_str = "",
                            comments = NULL, coef_rename = NULL) {

  lrt <- get_lrt(model)

  est <- tidy(model, effects = "fixed") |>
    filter(component == "cond") |>
    left_join(lrt, by = "term") |>
    mutate(
      IRR     = round(exp(estimate), 3),
      IRR     = if_else(term == "(Intercept)", NA_real_, IRR),
      cell    = paste0(round(estimate, 3), " (", round(std.error, 3), ")"),
      p.value = fmt_p_lrt(
        if_else(!is.na(p_lrt), fmt_p(p_lrt), fmt_p(p.value)), LRT
      ),
      term    = if (!is.null(coef_rename)) {
                  case_match(term, !!!coef_rename, .default = term)
                } else term
    ) |>
    select(term, cell, IRR, p.value)

  disp <- round(summary(model)$sigma, 3)

  re <- tidy(model, effects = "ran_pars") |>
    filter(component == "cond") |>
    mutate(
      term    = paste0("SD (", group, ")"),
      cell    = as.character(round(estimate, 3)),
      IRR     = NA_real_,
      p.value = NA_character_
    ) |>
    select(term, cell, IRR, p.value) |>
    mutate(IRR = as.character(IRR))

  notes <- c(
    paste0("Formula: ", formula_str),
    paste0("Dispersion: ", disp),
    "IRR = incidence rate ratio. SD = random effect standard deviation. The LRT p-value and statistic are reported where applicable."
  )
  if (!is.null(comments)) notes <- c(notes, comments)
  notes_combined <- paste(notes, collapse = "<br />")

  bind_rows(
    est |> mutate(IRR = as.character(IRR)),
    re
  ) |>
    mutate(
      IRR     = if_else(is.na(IRR) | IRR == "NA", "—", IRR),
      p.value = if_else(is.na(p.value), "—", p.value)
    ) |>
    gt() |>
    cols_label(
      term    = "Term",
      cell    = "Estimate (SE)",
      IRR     = "IRR",
      p.value = "p-value (LRT)"
    ) |>
    tab_header(title = title) |>
    tab_source_note(source_note = notes_combined) |>
    tab_options(
      table.width       = pct(100),
      source_notes.font.size = 11
    )
}

format_lmer <- function(model, title = "", formula_str = "",
                         comments = NULL, coef_rename = NULL) {

  lrt <- get_lrt(model)

  est <- tidy(model, effects = "fixed") |>
    left_join(lrt, by = "term") |>
    mutate(
      cell    = paste0(round(estimate, 3), " (", round(std.error, 3), ")"),
      p.value = fmt_p_lrt(
        if_else(!is.na(p_lrt), fmt_p(p_lrt), fmt_p(p.value)), LRT
      ),
      term    = if (!is.null(coef_rename)) {
                  case_match(term, !!!coef_rename, .default = term)
                } else term
    ) |>
    select(term, cell, p.value)

  re <- tidy(model, effects = "ran_pars") |>
    mutate(
      term    = paste0("SD (", group, ")"),
      cell    = as.character(round(estimate, 3)),
      p.value = NA_character_
    ) |>
    select(term, cell, p.value)

  sigma_val <- round(sigma(model), 3)

  notes <- c(
    paste0("Formula: ", formula_str),
    paste0("Residual SD: ", sigma_val),
    "SD = random effect standard deviation. The LRT p-value and statistic are reported where applicable."
  )
  if (!is.null(comments)) notes <- c(notes, comments)
  notes_combined <- paste(notes, collapse = "<br />")

  bind_rows(est, re) |>
    mutate(
      p.value = if_else(is.na(p.value), "—", p.value)
    ) |>
    gt() |>
    cols_label(
      term    = "Term",
      cell    = "Estimate (SE)",
      p.value = "p-value (LRT)"
    ) |>
    tab_header(title = title) |>
    tab_source_note(source_note = notes_combined) |>
    tab_options(
      table.width       = pct(100),
      source_notes.font.size = 11
    )
}
```


## Intrinsic Models
```{r}
# Store original lengths for backtransforming, and center `length` around 0 for better interpretation
length_means_original <- tapply(df_long$length, df_long$sex, mean)
df_long$length <- as.numeric(scale(df_long$length, scale = FALSE))
```

### Activity

```{r}
#| label: mdl-activity-intrinsic

activity_I <- glmmTMB(activity ~ sex + period + length + sex * period + 
                        (1 | fish_id) + (1 | group_id), 
                      family = nbinom2, ziformula = ~1, data = df_long)
check_model(activity_I)

format_glmmtmb(
  activity_I,
  title       = "Time Active (s) [Intrinsic Model]",
  formula_str = "activity ~ sex + period + length + sex × period + (1 | fish_id) + (1 | group_id), family = negative binomial",
  comments    = "Fish-level random effect variance was essentially zero; pair-level clustering accounted for most random variation.",
  coef_rename = list(
    "(Intercept)" ~ "Intercept",
    "sexMale" ~ "Sex (Male)",
    "periodPeriod 2" ~ "Period 2",
    "length" ~ "Body Length",
    "sexMale:periodPeriod 2" ~ "Sex (Male) × Period 2"
  )
)
```
Period was the only significant predictor of activity (p < 0.001), with activity approximately 2.4-fold higher in Period 2. Sex, body length, and the sex × period interaction were all non-significant (all p > 0.42), suggesting the difference between nudging periods was consistent across sexes and body sizes. Note that the fish-level random effect variance estimate was extremely small, suggesting pair-level clustering accounted for the majority of random variation.



### ANN
```{r ann_intrinsic}
ann_I <- glmmTMB(ann ~ sex + period + length + sex * period + (1 | fish_id), family = tweedie(link = "log"), data = df_long)

check_model(ann_I)

format_glmmtmb(
  ann_I,
  title       = "ANN (nudges/min active) [Intrinsic Model]",
  formula_str = "ann ~ sex + period + length + sex * period + (1 | fish_id), family = Tweedie",
  coef_rename = list(
    "(Intercept)" ~ "Intercept",
    "sexMale" ~ "Sex (Male)",
    "periodPeriod 2" ~ "Period 2",
    "length" ~ "Body Length",
    "sexMale:periodPeriod 2" ~ "Sex (Male) × Period 2"
  )
)
```


Both period (p = 1.45e-06) and the sex × period interaction (LRT = 10.736, p = 0.001) were significant predictors of ANN, with body length and sex regressors not being significant (both p > 0.28). The positive period effect (IRR ≈ 4.82) and negative sex × period interaction (IRR ≈ 0.19) together indicate that ANN increased substantially between periods for females, but these effects largely cancelled out for males, suggesting ANN remained relatively stable across periods for males.

### Respiratory Rate
```{r resp_intrinsic}

resp_I <- lmer(resp ~ sex + period + length + sex * period + (1 | fish_id) + (1 | group_id), REML = FALSE, na.action = na.omit, data = df_long)

check_model(resp_I)

format_lmer(
  resp_I,
  title       = "Resp. Rate (breaths/min) [Intrinsic Model]",
  formula_str = "resp ~ sex + period + length + sex × period + (1 | fish_id) + (1 | group_id), family = gaussian",
  comments    = "Fish-level random effect variance was essentially zero; pair-level clustering accounted for most random variation.",
  coef_rename = list(
    "(Intercept)" ~ "Intercept",
    "sexMale" ~ "Sex (Male)",
    "periodPeriod 2" ~ "Period 2",
    "length" ~ "Body Length",
    "sexMale:periodPeriod 2" ~ "Sex (Male) × Period 2"
  )
)
```

Respiratory rate declined significantly between periods (p = 6.82e-11), decreasing by approximately 18 breaths per minute on average. Sex, body length, and the sex × period interaction were all non-significant (all p > 0.39), indicating the period effect was consistent across sexes and body sizes. Note that a singular fit was observed for this model, with the fish-level random effect variance estimated at zero, suggesting pair-level clustering accounted for the majority of random variation.

### Wall Surfing
```{r surfing_intrinsic}

surfing_I <- glmmTMB(surfing ~ sex + period + length + sex * period + (1 | fish_id) + (1 | group_id), family = nbinom2, ziformula = ~1, data = df_long)

check_model(surfing_I)

format_glmmtmb(
  surfing_I,
  title       = "Wall Surfing (s) [Intrinsic Model]",
  formula_str = "surfing ~ sex + period + length + sex * period + (1 | fish_id) + (1 | group_id), family = negative binomial",
  comments    = "Fish-level random effect variance was essentially zero; pair-level clustering accounted for most random variation.",
  coef_rename = list(
    "(Intercept)" ~ "Intercept",
    "sexMale" ~ "Sex (Male)",
    "periodPeriod 2" ~ "Period 2",
    "length" ~ "Body Length",
    "sexMale:periodPeriod 2" ~ "Sex (Male) × Period 2"
  )
)
```
Period was a significant predictor of wall surfing (p = 0.016), with wall surfing approximately doubling between periods (IRR ≈ 2.07). Sex, body length, and the sex × period interaction were all non-significant (p > 0.21). As with the activity and respiration rate models, the fish-level random effect variance was essentially zero, with pair-level clustering accounting for the majority of random variation.

## Intrinsic Summary Table
```{r}
length_by_sex <- tapply(df_long$length, df_long$sex, mean)

intrinsic_tbl <- expand.grid(
  sex = c("Female", "Male"),
  period = c("Period 1", "Period 2"),
  fish_id = NA,
  group_id = NA
)
intrinsic_tbl$length <- length_by_sex[intrinsic_tbl$sex]

intrinsic_tbl$activity <- round(predict(activity_I, newdata = intrinsic_tbl, type = "response", re.form = NA), 3)
intrinsic_tbl$ann <- round(predict(ann_I, newdata = intrinsic_tbl, type = "response", re.form = NA), 3)
intrinsic_tbl$resp <- round(predict(resp_I, newdata = intrinsic_tbl, type = "response", re.form = NA), 3)
intrinsic_tbl$surfing <- round(predict(surfing_I, newdata = intrinsic_tbl, type = "response", re.form = NA), 3)
intrinsic_tbl$length <- round(length_means_original[intrinsic_tbl$sex], 3)
intrinsic_tbl$fish_id <- NULL
intrinsic_tbl$group_id <- NULL

intrinsic_tbl
```


## Intrinsic Multiple Comparisons Correction
The Benjamini-Hochberg (BH) correction was applied within each intrinsic model as the same set of predictors (sex, period, body length, and their interaction) was tested across all outcome variables. Given the small number of predictors per model (4), corrected p-values are reported in the tables below for transparency but raw p-values are used for interpretation in the narrative, as multiple comparisons correction over a small family of tests can be overly conservative.
```{r}
intrinsic_models <- list(
  Activity         = activity_I,
  ANN              = ann_I,
  `Resp Rate`      = resp_I,
  `Wall Surfing`   = surfing_I
)

fixed_terms <- c("periodPeriod 2",
                 "sexMale",
                 "sexMale:periodPeriod 2",
                 "length")

term_labels <- c("Period 2",
                  "Sex (Male)",
                  "Sex × Period 2",
                  "Length")

get_p <- function(mod, term_pat) {
  # First try drop1 for terms it can test
  d <- tryCatch(
    drop1(mod, test = "Chisq"),
    error = function(e) NULL
  )
  
  if (!is.null(d) && term_pat %in% rownames(d)) {
    p <- d[rownames(d) == term_pat, "Pr(Chi)"]
    if (length(p) > 0 && !is.na(p)) return(p)
  }
  
  # Fall back to summary z/t-tests for main effects blocked by hierarchy
  s <- tidy(mod, effects = "fixed")
  p <- s |> filter(term == term_pat) |> pull(p.value)
  if (length(p) == 0) NA_real_ else p
}

raw_p <- map_dfr(
  intrinsic_models,
  function(m) setNames(vapply(fixed_terms, get_p, numeric(1), mod = m),
                       fixed_terms),
  .id = "Behaviour"
)

adj_mat <- t(apply(raw_p[fixed_terms], 1,
                   \(p) p.adjust(p, method = "BH")))
colnames(adj_mat) <- paste0(fixed_terms, "_adj")

result_tbl <- bind_cols(raw_p, as.data.frame(adj_mat))
interleaved <- c(rbind(fixed_terms, paste0(fixed_terms, "_adj")))
result_tbl <- result_tbl[, c("Behaviour", interleaved)]

# Format p-values as scientific notation
result_tbl <- result_tbl |>
  mutate(across(-Behaviour, ~formatC(., format = "e", digits = 2)))

# Interleave "Term" and "Term (adj)"
col_labels <- c(rbind(term_labels, paste0(term_labels, " (adj)")))

kable(result_tbl,
      col.names = c("Behaviour", col_labels),
      caption = "Intrinsic model p-values (raw and BH-adjusted within model). Adjusted p-values computed using the Benjamini-Hochberg method.") |>
  kableExtra::kable_styling() |>
  kableExtra::add_header_above(c(" " = 1,
                                  "Period 2" = 2,
                                  "Sex (Male)" = 2,
                                  "Sex × Period 2" = 2,
                                  "Length" = 2))
```




## Behavioral Models
### Activity
```{r activity_behavioral}

activity_B <- glmmTMB(activity ~ period + ann + resp + surfing + (1 | fish_id) + (1 | group_id), family = nbinom2, ziformula = ~1, data = df_long)

check_model(activity_B)

format_glmmtmb(
  activity_B,
  title       = "Time Active (s) [Behavioral Model]",
  formula_str = "activity ~ period + ann + resp + surfing + (1 | fish_id) + (1 | group_id), family = negative binomial",
  comments    = "Fish-level random effect variance was essentially zero; pair-level clustering accounted for most random variation.",
  coef_rename = list(
    "(Intercept)" ~ "Intercept",
    "periodPeriod 2" ~ "Period 2",
    "ann" ~ "ANN (nudges/min active)",
    "resp" ~ "Resp. Rate (breaths/min)",
    "surfing" ~ "Wall Surfing (s)"
  )
)
```

Wall surfing was the only significant predictor of activity (LRT = 13.48, p < 0.001), with period, ANN, and respiration rate all non-significant. Moderate collinearity was detected for period (VIF between 5 and 10), though below the threshold warranting concern


### ANN
```{r ann_behavioral}

ann_B <- glmmTMB(ann ~ activity + resp + surfing + period + (1 | fish_id), family = tweedie(link = "log"), data = df_long)

check_model(ann_B)

format_glmmtmb(
  ann_B,
  title       = "ANN (nudges/min active) [Behavioral Model]",
  formula_str = "ann ~ activity + resp + surfing + period + (1 | fish_id), family = tweedie",
  coef_rename = list(
    "(Intercept)" ~ "Intercept",
    "periodPeriod 2" ~ "Period 2",
    "activity" ~ "Time Active (s)",
    "resp" ~ "Resp. Rate (breaths/min)",
    "surfing" ~ "Wall Surfing (s)"
  )
)
```
No predictors were significant in the ANN behavioral model, with period, activity, respiration rate, and wall surfing all non-significant (all p > 0.12). Some numerical warnings were produced during model fitting, likely reflecting the fact that none of the predictors were explaining meaningful variation in ANN.


### Respiratory Rate
```{r resp_behavioral}

resp_B <- lmer(resp ~ period + activity + ann + surfing + (1 | fish_id) + (1 | group_id), REML = FALSE, na.action = na.omit, data = df_long)

check_model(resp_B)

format_lmer(
  resp_B,
  title       = "Resp. Rate (breaths/min) [Behavioral Model]",
  formula_str = "resp ~ period + activity + ann + surfing + (1 | fish_id) + (1 | group_id), family = gaussian",
  comments    = "Fish-level random effect variance was essentially zero; pair-level clustering accounted for most random variation.",
  coef_rename = list(
    "(Intercept)" ~ "Intercept",
    "periodPeriod 2" ~ "Period 2",
    "activity" ~ "Time Active (s)",
    "ann" ~ "ANN (nudges/min active)",
    "surfing" ~ "Wall Surfing (s)"
  )
)
```
Period and wall surfing were both significant predictors of respiration rate (LRT = 63.02, p < 0.001 and LRT = 5.95, p = 0.015 respectively), with respiration rate declining substantially between periods and increasing slightly with wall surfing. Activity and ANN were non-significant. The fish-level random effect variance was again zero, consistent with the pattern seen in other models."


### Wall Surfing
```{r surfing_behavioral}

surfing_B <- glmmTMB(surfing ~ period + activity + ann + resp + (1 | fish_id) + (1 | group_id), family = nbinom2, ziformula = ~1, data = df_long)

check_model(surfing_B)

format_glmmtmb(
  surfing_B,
  title       = "Wall Surfing (s) [Behavioral Model]",
  formula_str = "surfing ~ period + activity + ann + resp + (1 | fish_id) + (1 | group_id), family = negative binomial",
  comments    = "Both fish-level and group-level random effect variances were essentially zero, suggesting wall surfing variation in this model was largely explained by the fixed effects alone.",
  coef_rename = list(
    "(Intercept)" ~ "Intercept",
    "periodPeriod 2" ~ "Period 2",
    "activity" ~ "Time Active (s)",
    "ann" ~ "ANN (nudges/min active)",
    "resp" ~ "Resp. Rate (breaths/min)"
  )
)
```
Period and activity were significant predictors of wall surfing (LRT = 6.10, p = 0.014 and LRT = 11.74, p < 0.001 respectively), with wall surfing increasing between periods and positively associated with activity. Respiratory rate was marginally non-significant (LRT = 3.73, p = 0.053) and ANN was non-significant. Notably, both random effect variances were essentially zero in this model, suggesting wall surfing variation was largely explained by the fixed effects alone.


## Behavioral Summary Table
```{r}
behavioral_tbl <- df_long |>
  group_by(sex, period) |>
  summarise(
    activity = mean(activity, na.rm = TRUE),
    ann      = mean(ann,      na.rm = TRUE),
    resp     = mean(resp,     na.rm = TRUE),
    surfing  = mean(surfing,  na.rm = TRUE),
    .groups  = "drop"
  ) |>
  mutate(fish_id = NA, group_id = NA)

behavioral_tbl$activity_pred <- round(predict(activity_B, newdata = behavioral_tbl, type = "response", re.form = NA), 3)
behavioral_tbl$ann_pred      <- round(predict(ann_B,      newdata = behavioral_tbl, type = "response", re.form = NA), 3)
behavioral_tbl$resp_pred     <- round(predict(resp_B,     newdata = behavioral_tbl, type = "response", re.form = NA), 3)
behavioral_tbl$surfing_pred  <- round(predict(surfing_B,  newdata = behavioral_tbl, type = "response", re.form = NA), 3)

behavioral_tbl |>
  select(sex, period, activity_pred, ann_pred, resp_pred, surfing_pred) |>
  kable(col.names = c("Sex", "Period", "Activity (s)", "ANN (nudges/min)", "Resp Rate (breaths/min)", "Wall Surfing (s)"),
        caption = "Predicted behavioral values at sex- and period-specific mean predictor values.") |>
  kableExtra::kable_styling() |>
  kableExtra::collapse_rows(columns = 1, valign = "top")
```

## Behavioral Multiple Comparisons Correction
A multiple comparisons correction was not applied to the behavioral models as the predictor sets differ across outcome variables.

## Lagged Models
### Activity
```{r activity_lagged}

activity_L <- glmmTMB(activity_second ~ activity_first + ann_first + resp_first + surfing_first + (1 | group_id), 
                      family = nbinom2, ziformula = ~1, data = df)

check_model(activity_L)

dropterm(activity_L, test = "Chisq")

format_glmmtmb(
  activity_L,
  title       = "Time Active in Period 2 (s) [Lagged Model]",
  formula_str = "activity_second ~ activity_first + ann_first + resp_first + surfing_first + (1 | group_id), family = negative binomial",
  coef_rename = list(
    "(Intercept)" ~ "Intercept",
    "activity_first" ~ "P1 Activity (s)",
    "ann_first" ~ "P1 ANN (nudges/min active)",
    "resp_first" ~ "P1 Resp. Rate (breaths/min)",
    "surfing_first" ~ "P1 Wall Surfing (s)"
  )
)
```
Model fit for the activity lagged model was poor, reflected by an extremely large dispersion parameter (5.7 × 10⁸), likely due to the 300-second activity ceiling imposed by monitoring for a set time period in Period 2, creating a distributional shape the negative binomial could not accommodate. Results from this model should be interpreted with caution. No Period 1 predictors were significant.


### ANN
```{r ann_lagged}

ann_L <- glmmTMB(ann_second ~ activity_first + ann_first + resp_first + surfing_first + (1 | group_id), family = tweedie(link = "log"), data = df)

check_model(ann_L)

format_glmmtmb(
  ann_L,
  title       = "ANN in Period 2 (nudges/min active) [Lagged Model]",
  formula_str = "ann_second ~ activity_first + ann_first + resp_first + surfing_first + (1 | group_id), family = tweedie",
  coef_rename = list(
    "(Intercept)" ~ "Intercept",
    "activity_first" ~ "P1 Activity (s)",
    "ann_first" ~ "P1 ANN (nudges/min active)",
    "resp_first" ~ "P1 Resp. Rate (breaths/min)",
    "surfing_first" ~ "P1 Wall Surfing (s)"
  )
)
```
No nudging period 1 predictors were significant in the lagged ANN model (all p > 0.11, suggesting that nudging rate while active in nudging period 2 was not meaningfully predicted by any nudging period 1 behavioral measures.

### Respiratory Rate
```{r resp_lagged}
resp_L <- lmer(resp_second ~ activity_first + ann_first + resp_first + surfing_first + (1 | group_id), REML = FALSE, na.action = na.omit, data = df_complete_resp)

check_model(resp_L)

format_lmer(
  resp_L,
  title       = "Resp. Rate in Period 2 (breaths/min) [Lagged Model]",
  formula_str = "resp_second ~ activity_first + ann_first + resp_first + surfing_first + (1 | group_id), family = gaussian",
  coef_rename = list(
    "(Intercept)" ~ "Intercept",
    "activity_first" ~ "P1 Activity (s)",
    "ann_first" ~ "P1 ANN (nudges/min active)",
    "resp_first" ~ "P1 Resp. Rate (breaths/min)",
    "surfing_first" ~ "P1 Wall Surfing (s)"
  )
)
```
Period 1 wall surfing showed a marginal positive association with Period 2 respiration rate (LRT = 3.74, p = 0.053), while activity, ANN, and Period 1 respiration rate were all non-significant (all p > 0.21). This model was fit on 35 individuals due to missing nudging period 2 respiration data in 3 fish.


### Wall Surfing
```{r surfing_lagged}

surfing_L <- glmmTMB(surfing_second ~ activity_first + ann_first + resp_first + surfing_first + (1 | group_id), data = df, family = nbinom2, ziformula = ~1)

check_model(surfing_L)

format_glmmtmb(
  surfing_L,
  title       = "Wall Surfing in Period 2 (s) [Lagged Model]",
  formula_str = "surfing_second ~ activity_first + ann_first + resp_first + surfing_first + (1 | group_id), family = negative binomial",
  coef_rename = list(
    "(Intercept)" ~ "Intercept",
    "activity_first" ~ "P1 Activity (s)",
    "ann_first" ~ "P1 ANN (nudges/min active)",
    "resp_first" ~ "P1 Resp. Rate (breaths/min)",
    "surfing_first" ~ "P1 Wall Surfing (s)"
  )
)
```

Period 1 ANN and Period 1 respiration rate were both significant negative predictors of Period 2 wall surfing (LRT = 7.11, p = 0.008 and LRT = 16.35, p < 0.001 respectively), suggesting that fish with higher nudging rates while active and higher respiration rates in Period 1 showed less wall surfing in Period 2. Period 1 activity and Period 1 wall surfing were both non-significant (p > 0.19).


## Lagged Summary Table
```{r}
lagged_tbl <- df |>
  group_by(sex) |>
  summarise(
    activity_first = mean(activity_first, na.rm = TRUE),
    ann_first      = mean(ann_first,      na.rm = TRUE),
    resp_first     = mean(resp_first,     na.rm = TRUE),
    surfing_first  = mean(surfing_first,  na.rm = TRUE),
    .groups = "drop"
  ) |>
  mutate(group_id = NA)

lagged_tbl$activity_pred <- round(predict(activity_L, newdata = lagged_tbl, type = "response", re.form = NA), 3)
lagged_tbl$ann_pred      <- round(predict(ann_L,      newdata = lagged_tbl, type = "response", re.form = NA), 3)
lagged_tbl$resp_pred     <- round(predict(resp_L,     newdata = lagged_tbl, type = "response", re.form = NA), 3)
lagged_tbl$surfing_pred  <- round(predict(surfing_L,  newdata = lagged_tbl, type = "response", re.form = NA), 3)

lagged_tbl |>
  select(sex, activity_pred, ann_pred, resp_pred, surfing_pred) |>
  kable(col.names = c("Sex", "Activity (s)", "ANN", "Resp Rate", "Wall Surfing (s)"),
        caption = "Predicted nudging period 2 behavioral values at sex-specific mean nudging period 1 predictor values. Sex differences in predictions reflect differences in period 1 predictor means rather than a sex effect in the models.") |>
  kableExtra::kable_styling()
```

## Lagged Multiple Comparisons

BH correction was applied within each lagged model as the same set of Period 1 predictors (activity, ANN, respiration rate, and wall surfing) was tested across all Period 2 outcome variables. As with the intrinsic models, corrected p-values are reported in the tables below for transparency but raw p-values are used for interpretation in the narrative given the small family size.

```{r}
lagged_models <- list(
  Activity         = activity_L,
  ANN              = ann_L,
  `Resp Rate`      = resp_L,
  `Wall Surfing`   = surfing_L
)

fixed_terms_L <- c("activity_first",
                 "ann_first",
                 "resp_first",
                 "surfing_first")

term_labels_L <- c("P1 Activity",
                  "P1 ANN",
                  "P1 Resp. Rate",
                  "P1 Wall Surfing")

raw_p_L <- map_dfr(
  lagged_models,
  function(m) setNames(vapply(fixed_terms_L, get_p, numeric(1), mod = m),
                       fixed_terms_L),
  .id = "Behaviour"
)

adj_mat_L <- t(apply(raw_p_L[fixed_terms_L], 1,
                   \(p) p.adjust(p, method = "BH")))
colnames(adj_mat_L) <- paste0(fixed_terms_L, "_adj")

result_tbl_L <- bind_cols(raw_p_L, as.data.frame(adj_mat_L))
interleaved_L <- c(rbind(fixed_terms_L, paste0(fixed_terms_L, "_adj")))
result_tbl_L <- result_tbl_L[, c("Behaviour", interleaved_L)]

# Format p-values as scientific notation
result_tbl_L <- result_tbl_L |>
  mutate(across(-Behaviour, ~formatC(., format = "e", digits = 2)))

# Interleave "Term" and "Term (adj)"
col_labels_L <- c(rbind(term_labels_L, paste0(term_labels_L, " (adj)")))

kable(result_tbl_L,
      col.names = c("Behaviour", col_labels_L),
      caption = "Lagged model p-values (raw and BH-adjusted within model). Adjusted p-values computed using the Benjamini-Hochberg method.") |>
  kableExtra::kable_styling() |>
  kableExtra::add_header_above(c(" " = 1,
                                  "P1 Activity" = 2,
                                  "P1 ANN" = 2,
                                  "P1 Resp. Rate" = 2,
                                  "P1 Wall Surfing" = 2))
```



# Foraging Period Models
## Predictor Selection
Foraging period models included only Period 2 behavioral predictors, as the foraging trial occurred immediately following Period 2, making these the most relevant behavioral measures for predicting foraging outcomes. Period 1 behaviors were excluded to avoid redundancy with Period 2 measures and to keep the number of predictors manageable given the sample size, as including too many predictors relative to observations risks overfitting (Harrell, 2015). Respiration rate was excluded from global models as it did not appear in any top candidate models (ΔAICc < 2) in preliminary analyses including it as a candidate predictor, allowing retention of the full sample of 38 individuals. Sex and body length were included as covariates given their potential influence on foraging behavior independent of nudging period behaviors.
### Feed Time
```{r}
# Dredge/averaged model selection
options(na.action = "na.fail")  # required for dredge

global_feed_mod <- glmmTMB(feed_time ~ sex + scale(length) +
                              scale(activity_second) + scale(ann_second) + scale(resp_second) + 
                              scale(surfing_second) + scale(activity_first) + scale(ann_first) + scale(surfing_first) + scale(resp_first) + (1 | group_id),
                            data = df_complete_resp, family = nbinom2)

# Run dredge to enumerate all subsets and compute AICc:
feed_dredged <- dredge(global_feed_mod, rank = "AICc")

# Take a look at the top models:
head(feed_dredged, 10)

# Subset AICc < 2
feed_top_set <- get.models(feed_dredged, subset = delta < 2)

# Do model‐averaging over that set:
feed_avg_mod <- model.avg(feed_top_set)

# Summarize averaged coefficients & relative importance:
summary(feed_avg_mod)

# Extract variable importance (sum of weights across models where they appear):
sw(feed_avg_mod)
```

```{r}
# Dredge/averaged model selection
options(na.action = "na.fail")  # required for dredge

global_feed_mod_2 <- glmmTMB(feed_time ~ sex + scale(length) +
                              scale(activity_second) + scale(ann_second) +
                              scale(surfing_second) + scale(activity_first) + scale(ann_first) + scale(surfing_first) + scale(resp_first) + (1 | group_id),
                            data = df, family = nbinom2)

# Run dredge to enumerate all subsets and compute AICc:
feed_dredged_2 <- dredge(global_feed_mod_2, rank = "AICc")

# Take a look at the top models:
head(feed_dredged_2, 10)

# Subset AICc < 2
feed_top_set_2 <- get.models(feed_dredged_2, subset = delta < 2)

# Do model‐averaging over that set:
feed_avg_mod_2 <- model.avg(feed_top_set_2)

# Summarize averaged coefficients & relative importance:
summary(feed_avg_mod_2)

# Extract variable importance (sum of weights across models where they appear):
sw(feed_avg_mod_2)
```

```{r}
feed_mod_p2 <- glmmTMB(feed_time ~ activity_second + ann_first + (1 | group_id),
                        data = df, family = nbinom2)

check_model(feed_mod_p2)

format_glmmtmb(
  feed_mod_p2,
  title       = "Time to Find Food (s)",
  formula_str = "feed_time ~ activity_second + ann_first + (1 | group_id), family = negative binomial",
  coef_rename = list(
    "(Intercept)" ~ "Intercept",
    "activity_second" ~ "P2 Activity (s)",
    "ann_first" ~ "P1 ANN (nudges/min active)"
  )
)
```
Period 2 activity was a significant negative predictor of feed time (LRT = 8.70, p = 0.003), with more active fish taking less time to reach and consume food (IRR = 0.995 per second of activity). While the per-second effect is small, it is meaningful across the observed range of activity values.




### Freeze Time
```{r}
# Dredge/averaged model selection
options(na.action = "na.fail") 

global_freeze_mod <- glmmTMB(freeze_time ~ sex + scale(length) +
                                scale(activity_second) + scale(ann_second) + scale(resp_second) + 
                                scale(surfing_second) + scale(activity_first) + scale(ann_first) + scale(surfing_first) + scale(resp_first) + (1 | group_id),
                             data = df_complete_resp, family = nbinom2)

# Run dredge to enumerate all subsets and compute AICc:
freeze_dredged <- dredge(global_freeze_mod, rank = "AICc")

# Take a look at the top models:
head(freeze_dredged, 10)

# Subset so AICc < 2
freeze_top_set <- get.models(freeze_dredged, subset = delta < 2)

# Do model‐averaging over that set:
freeze_avg_mod <- model.avg(freeze_top_set)

# Summarize averaged coefficients & relative importance:
summary(freeze_avg_mod)

# Extract variable importance (sum of weights across models where they appear):
sw(freeze_avg_mod)
```

```{r}
# Dredge/averaged model selection
options(na.action = "na.fail") 

global_freeze_mod_2 <- glmmTMB(freeze_time ~ sex + scale(length) +
                                scale(activity_second) + scale(ann_second) +
                                scale(surfing_second) + scale(activity_first) + scale(ann_first) + scale(surfing_first) + scale(resp_first) + (1 | group_id),
                             data = df, family = nbinom2)

# Run dredge to enumerate all subsets and compute AICc:
freeze_dredged_2 <- dredge(global_freeze_mod_2, rank = "AICc")

# Take a look at the top models:
head(freeze_dredged_2, 10)

# Subset so AICc < 2
freeze_top_set_2 <- get.models(freeze_dredged_2, subset = delta < 2)

# Do model‐averaging over that set:
freeze_avg_mod_2 <- model.avg(freeze_top_set_2)

# Summarize averaged coefficients & relative importance:
summary(freeze_avg_mod_2)

# Extract variable importance (sum of weights across models where they appear):
sw(freeze_avg_mod_2)
```
```{r}
freeze_mod_p2 <- glmmTMB(freeze_time ~ activity_first + (1 | group_id),
                          data = df, family = nbinom2)

check_model(freeze_mod_p2)

format_glmmtmb(
  freeze_mod_p2,
  title       = "Freeze Time During Foraging (s)",
  formula_str = "freeze_time ~ activity_first + (1 | group_id), family = negative binomial",
  coef_rename = list(
    "(Intercept)" ~ "Intercept",
    "activity_first" ~ "P1 Activity (s)"
  )
)
```

# Appendices

## Discriminant Validity

To assess whether wall surfing and activity were measuring the same underlying behavior, we examined their correlation, variance inflation factors (VIF) when included together as predictors, and factor loadings. VIF values below 10 are generally considered acceptable, while values above 5 suggest meaningful collinearity.
### Wall Surfing and Activity

```{r}
cor_ws_first  <- cor.test(df$surfing_first,  df$activity_first)
cor_ws_second <- cor.test(df$surfing_second, df$activity_second)
print(cor_ws_first)
print(cor_ws_second)

lm_ws_first  <- lm(feed_time ~ activity_first  + surfing_first,  data = df)
lm_ws_second <- lm(feed_time ~ activity_second + surfing_second, data = df)
print(check_collinearity(lm_ws_first))
print(check_collinearity(lm_ws_second))

behavior_ws_first  <- df |> select(activity_first,  surfing_first,  nudges_first)
behavior_ws_second <- df |> select(activity_second, surfing_second, nudges_second)
fa_ws_first  <- fa(behavior_ws_first,  nfactors = 2, rotate = "varimax")
fa_ws_second <- fa(behavior_ws_second, nfactors = 2, rotate = "varimax")
print(fa_ws_first$loadings)
print(fa_ws_second$loadings)
```
Wall surfing and activity were moderately correlated in Period 1 (r = 0.50, p = 0.002) and strongly correlated in Period 2 (r = 0.86, p < 0.001), with VIF values of 1.32 and 3.93 respectively — both below conventional thresholds but notably higher in Period 2. The substantial change in correlation between periods suggests the two variables are not simply redundant measures of the same construct, as a consistent relationship would be expected if they were measuring the same underlying behavior. Factor analysis indicated that the two variables did not load cleanly onto separate factors in either period, suggesting partial overlap. Given the strong Period 2 correlation, models including both variables simultaneously should be interpreted with caution, though collinearity was not severe enough to preclude their joint inclusion."

### Wall Surfing and Respiration Rate

```{r}
cor_wsrr_first  <- cor.test(df$surfing_first,  df$resp_first)
cor_wsrr_second <- cor.test(df$surfing_second, df$resp_second)
print(cor_wsrr_first)
print(cor_wsrr_second)

lm_wsrr_first  <- lm(feed_time ~ resp_first  + surfing_first,  data = df)
lm_wsrr_second <- lm(feed_time ~ resp_second + surfing_second, data = df_complete_resp)
print(check_collinearity(lm_wsrr_first))
print(check_collinearity(lm_wsrr_second))

behavior_wsrr_first  <- df |> select(resp_first,  surfing_first,  nudges_first)
behavior_wsrr_second <- df |> select(resp_second, surfing_second, nudges_second)
fa_wsrr_first  <- fa(behavior_wsrr_first,  nfactors = 2, rotate = "varimax")
fa_wsrr_second <- fa(behavior_wsrr_second, nfactors = 2, rotate = "varimax")
print(fa_wsrr_first$loadings)
print(fa_wsrr_second$loadings)
```

### ANN and Activity

```{r}
cor_ann_first  <- cor.test(df$ann_first,  df$activity_first)
cor_ann_second <- cor.test(df$ann_second, df$activity_second)
print(cor_ann_first)
print(cor_ann_second)

lm_ann_first  <- lm(feed_time ~ activity_first  + ann_first,  data = df)
lm_ann_second <- lm(feed_time ~ activity_second + ann_second, data = df)
print(check_collinearity(lm_ann_first))
print(check_collinearity(lm_ann_second))

behavior_ann_first  <- df |> select(activity_first,  ann_first,  surfing_first)
behavior_ann_second <- df |> select(activity_second, ann_second, surfing_second)
fa_ann_first  <- fa(behavior_ann_first,  nfactors = 2, rotate = "varimax")
fa_ann_second <- fa(behavior_ann_second, nfactors = 2, rotate = "varimax")
print(fa_ann_first$loadings)
print(fa_ann_second$loadings)
```
The same analyses were conducted to assess whether nudging rate while active (ANN) and activity were measuring the same underlying behavior. ANN and activity were essentially uncorrelated in both periods (Period 1: r = −0.12, p = 0.491; Period 2: r = 0.01, p = 0.953), with VIF values of approximately 1.0 indicating no collinearity. Factor analysis confirmed that ANN and activity loaded onto distinct factors, supporting their treatment as independent behavioral measures in subsequent analyses.


# Figures and Tables
```{r}
#| include: false
# ── Data and model export ─────────────────────────────────────────────────────
# Run this chunk to save all objects needed for figure generation to an RData
# file. 
# To load instead of re-running analysis, replace the source() call in setup
# with: load("figure_data.RData")

save(
  # Datasets
  df,
  df_long,
  df_complete_resp,
  plotdat,           # imputed respiration data for trend plot

  # Fitted models (needed if you want to add model-based prediction lines)
  feed_mod_p2,
  freeze_mod_p2,
  surfing_B,
  resp_B,
  surfing_L,

  file = "figure_data.RData"
)

message("Exported figure_data.RData — ", format(file.info("figure_data.RData")$size / 1024, digits = 3), " KB")
```


## Descriptive Statistics Table

```{r}
#| label: tbl-desc-stats

make_desc_paper <- function(data, vars, var_labels, period_label) {
  data |>
    summarise(
      across(all_of(vars),
             ~paste0(round(mean(., na.rm = TRUE), 2),
                    " (", round(sd(., na.rm = TRUE), 2), ")",
                    " [", round(min(., na.rm = TRUE), 2),
                    "–", round(max(., na.rm = TRUE), 2), "]")),
      .groups = "drop"
    ) |>
    pivot_longer(everything(), names_to = "variable", values_to = "summary") |>
    mutate(
      variable = var_labels[variable],
      period   = period_label
    )
}

p1_simple <- make_desc_paper(df,
  c("activity_first", "ann_first", "nudges_first", "resp_first", "surfing_first"),
  c(activity_first = "Activity (s)", ann_first = "ANN", nudges_first = "Nudges",
    resp_first = "Resp Rate", surfing_first = "Wall Surfing (s)"),
  "Period 1")

p2_simple <- make_desc_paper(df,
  c("activity_second", "ann_second", "nudges_second", "resp_second", "surfing_second"),
  c(activity_second = "Activity (s)", ann_second = "ANN", nudges_second = "Nudges",
    resp_second = "Resp Rate", surfing_second = "Wall Surfing (s)"),
  "Period 2")

length_simple <- make_desc_paper(df,
  c("length"),
  c(length = "Length (cm)"),
  "—")

foraging_simple <- make_desc_paper(df,
  c("feed_time", "freeze_time"),
  c(feed_time = "Feed Time (s)", freeze_time = "Freeze Time (s)"),
  "Foraging")

bind_rows(p1_simple, p2_simple, foraging_simple, length_simple) |>
  gt() |>
  cols_label(
    variable = "Variable",
    period   = "Period",
    summary  = "Mean (SD) [Min–Max]"
  ) |>
  tab_header(title = "Descriptive statistics by monitoring period") |>
  tab_row_group(label = "Freeze Time (s)",  rows = variable == "Freeze Time (s)") |>
  tab_row_group(label = "Feed Time (s)",    rows = variable == "Feed Time (s)") |>
  tab_row_group(label = "Wall Surfing (s)", rows = variable == "Wall Surfing (s)") |>
  tab_row_group(label = "Resp Rate",        rows = variable == "Resp Rate") |>
  tab_row_group(label = "Nudges",           rows = variable == "Nudges") |>
  tab_row_group(label = "ANN",              rows = variable == "ANN") |>
  tab_row_group(label = "Activity (s)",     rows = variable == "Activity (s)") |>
  tab_row_group(label = "Length (cm)",      rows = variable == "Length (cm)") |>
  cols_hide(variable) |>
  tab_style(
    style     = cell_text(weight = "bold"),
    locations = cells_row_groups()
  ) |>
  tab_source_note("Values shown as mean (SD) [min–max].") |>
  tab_options(table.width = pct(100))
```

## Respiration Rate Trends Plot

```{r}
rr_plot <- ggplot(plotdat,
       aes(x = period, y = resp, group = interaction(group_id, fish_id),
           color = fish_id)) +
  geom_line(linewidth = 0.7, alpha = .65) +
  geom_point(aes(shape = point_type, fill = point_type),
             size = 3, stroke = 0.3) +
  scale_shape_manual(values = c(Observed = 21, Imputed = 24), name = NULL) +
  scale_fill_manual(values  = c(Observed = "black", Imputed = "orange"), name = NULL) +
  labs(x = NULL,
       y = "Respiratory rate (breaths/minute)",
       shape = NULL) +
  guides(color = "none") +
  theme_minimal(base_size = 20) +
  theme(legend.position = c(0.85, 0.91),
        legend.background = element_rect(fill = "white", color = "black"))

ggsave("figures/resp_trend.png", plot = rr_plot, width = 7, height = 5, dpi = 600)
ggsave("figures/svg/resp_trend.svg", plot = rr_plot, width = 7, height = 5, device = "svg")
rr_plot
```

## Between Period Contrast Plot
```{r}
# Get relevant data
plot_btwn_prd <- df_long |>
  select(fish_id, period, activity, ann, surfing, resp) |>
  pivot_longer(cols = -c(fish_id, period),
               names_to  = "behaviour",
               values_to = "value") |>
  mutate(
    period = factor(
      case_match(period,
        "Period 1" ~ "Nudging Period 1",
        "Period 2" ~ "Nudging Period 2"),
      levels = c("Nudging Period 1", "Nudging Period 2")),
    behaviour_f = factor(
      behaviour,
      levels = c("activity", "ann", "surfing", "resp"),
      labels = c("Activity", "ANN", "Wall Surfing", "Respiration Rate")
    )
  )

make_panel <- function(df, beh_name, y_lab) {
  ggplot(df |> filter(behaviour_f == beh_name),
         aes(x = period, y = value, fill = period)) +
    stat_boxplot(geom = "errorbar", width = 0.25) +
    geom_boxplot(outlier.shape = 21, width = 0.6, alpha = 0.7) +
    scale_fill_manual(values = c("#1f77b4", "#ff7f0e"), guide = "none") +
    labs(x = NULL, y = y_lab, title = beh_name) +
    theme_minimal(base_size = 12) +
    theme(plot.title = element_text(size = 15, hjust = 0.5))
}

p_act  <- make_panel(plot_btwn_prd, "Activity",         "Seconds")
p_ann  <- make_panel(plot_btwn_prd, "ANN",              "Nudges/min active")
p_surf <- make_panel(plot_btwn_prd, "Wall Surfing",     "Seconds")
p_resp <- make_panel(plot_btwn_prd, "Respiration Rate", "Breaths/min")

p_grid <- p_act / p_ann / p_surf / p_resp +
          plot_layout(guides = "collect")

ggsave("figures/period_behaviour.png",
       plot = p_grid, width = 4, height = 10, dpi = 600)
ggsave("figures/svg/period_behaviour.svg",
       plot = p_grid, width = 4, height = 10, device = "svg")

p_grid
```

## Wall Surfing Figure
```{r}
nb_smooth <- function(...) {
  geom_smooth(method = MASS::glm.nb,
              se     = TRUE,
              fullrange = FALSE,
              method.args = list(init.theta = 1),
              ...)
}

clr_vals <- c("#1f77b4", "#ff7f0e")
period_labs <- c("Nudging Period 1", "Nudging Period 2")

p_resp_surf <- ggplot(df_long,
                      aes(resp, surfing,
                          colour   = period,
                          linetype = period)) +
  geom_point(size = 2, alpha = .8) +
  nb_smooth() +
  scale_colour_manual(values = clr_vals, labels = period_labs, name = NULL) +
  scale_linetype_manual(values = c("solid", "dashed"), guide = "none") +
  labs(x = "Respiration rate (breaths/min)",
       y = "Wall surfing (s)",
       title = "A  Respiration–wall surfing relationship") +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom")

p_ann_surf <- ggplot(df, aes(ann_first, surfing_second)) +
  geom_point(size = 2, alpha = .8) +
  geom_smooth(method = "loess", se = TRUE) +
  coord_cartesian(xlim = c(0, 12)) +
  labs(x = "ANN in Nudging Period 1 (nudges / minute active)",
       y = "Wall surfing in Nudging Period 2 (s)",
       title = "B  Period 1 ANN–Period 2 wall surfing relationship") +
  theme_minimal(base_size = 11)

figure_ws <- p_resp_surf | p_ann_surf

ggsave("figures/wall_surf_revised.png",
       figure_ws, width = 9, height = 4, dpi = 600)
ggsave("figures/svg/wall_surf_revised.svg",
       figure_ws, width = 9, height = 4, device = "svg")

figure_ws
```

## Foraging Figure


```{r}
p_feed_act <- ggplot(df, aes(activity_second, feed_time)) +
  geom_point(size = 2, alpha = .8) +
  geom_smooth(method = MASS::glm.nb,
              se = TRUE,
              fullrange = FALSE,
              method.args = list(init.theta = 1)) +
  labs(x = "Activity in Nudging Period 2 (s)",
       y = "Latency to feed (s)",
       title = "A  Activity–foraging latency") +
  theme_minimal(base_size = 11) +
  theme(legend.position = "none")

p_feed_ann <- ggplot(df, aes(ann_first, feed_time)) +
  geom_point(size = 2, alpha = .8) +
  geom_smooth(method = MASS::glm.nb,
              se = TRUE,
              fullrange = FALSE,
              method.args = list(init.theta = 1)) +
  coord_cartesian(xlim = c(0, 12)) +
  labs(x = "ANN in Nudging Period 1 (nudges / minute active)",
       y = "Latency to feed (s)",
       title = "B  Period 1 ANN–foraging latency") +
  theme_minimal(base_size = 11) +
  theme(legend.position = "none")

figure_foraging <- p_feed_act / p_feed_ann

ggsave("figures/foraging_revised.png",
       figure_foraging, width = 5, height = 8, dpi = 600)
ggsave("figures/svg/foraging_revised.svg",
       figure_foraging, width = 5, height = 8, device = "svg")
ggsave("figures/foraging_revised.jpg",
       figure_foraging, width = 5, height = 8, dpi = 600)

figure_foraging
```